---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Rtins: Tools for Reading and Parsing Network Packet Capture (PCAP) Files in R

The **Rtins** package provides tools for analysing network captures in R on top of [`libtins`](http://libtins.github.io), a high-level, multiplatform C++ network packet decoding and crafting library.

## Installation

You need to install the [`libtins`](http://libtins.github.io) library first. And as a minimum requirement, `libtins` needs the development package of `libpcap` (or `WinPcap` for Windows). On Linux,

```{bash, eval=FALSE}
# install libpcap-devel, openssl-devel is also recommended
git clone https://github.com/mfontanini/libtins.git
mkdir libtins/build
cd libtins/build
cmake .. -DCMAKE_INSTALL_PREFIX=/usr
make
sudo make install
```

Please, refer to the `libtins` documentation for the installation in other platforms. Then, `Rtins` can be installed using `devtools`:

```{r, eval=FALSE}
devtools::install_github("Enchufa2/Rtins")
```

## Usage

```{r}
library(Rtins)

fname <- system.file("pcaps/http.cap", package="Rtins")
pcap <- read_pcap(fname)
head(pcap)
summary(pcap)
head(read_pcap(fname, "udp port 53"))
```
